---
title: "Lab 03 - Nobel laureates"
author: "Noah Booker"
date: "03/17/25"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1
```{r glimpse}
glimpse(nobel)
```

The glimpse functions allows to see that this dataset has 935 rows (observations; nobel laureates)
and 26 columns (variables).


### Exercise 2

```{r newdataframe}
nobel_living <- nobel %>% 
  filter(
    is.na(died_date),
    !is.na(country),
    gender != "org")
glimpse(nobel_living)
```
Created a new data frame called nobel_living which includes only nobel winners wha haven't died,
for whom country is available, and who are not an organization.

### Exercise 3

```{r barplot}
nobel_living <- nobel_living %>%
  mutate(
    country_us = if_else(country == "USA", "USA", "Other")
  )
nobel_living_science <- nobel_living %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))
ggplot(nobel_living_science, aes(x = country_us)) +
  geom_bar() +
  facet_wrap(~ category) +
  coord_flip()
```

In the barplot, we see that, for each category, most living Nobel laureates were based in the US
when they won their prizes. This aligns with the Buzzfeed article's claim.


### Exercise 4
```{r born_us}
nobel_living_science <- nobel_living_science %>% 
  mutate(
    born_country_us = if_else(born_country == "USA", "USA", "Other")
  )
nobel_living_science %>% 
  count(born_country_us)
```

105 winners were born in the US, and 123 were born elsewhere.

### Exercise 5

...

### Exercise 6

...
