---
title: "Lab 03 - Nobel laureates"
author: "Noah Booker"
date: "03/17/25"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1
```{r glimpse}
glimpse(nobel)
```

The glimpse functions allows to see that this dataset has 935 rows (observations; nobel laureates)
and 26 columns (variables).


### Exercise 2

```{r newdataframe}
nobel_living <- nobel %>% 
  filter(
    is.na(died_date),
    !is.na(country),
    gender != "org")
glimpse(nobel_living)
```
Created a new data frame called nobel_living which includes only nobel winners wha haven't died,
for whom country is available, and who are not an organization.

### Exercise 3

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...
